A Dependently Typed Multi-Stage Calculus \ifnotanonymous\thanks{Supported by organization x.}\fi

### 2019-06-11 main.tex
Revise the paragraph of Types.

A type is a type variable which is declared in the signature, a dependent function type,
an application of a term to a dependent function type, a code type, or an $\alpha$-closed type.
A dependent type $\Pi x:\tau.\tau$ is a type depending on values such as a vector with its length.
A function type in ordinary type systems is omitted because it is a specialized case of a dependent type.
A code type $\TW_\alpha \tau$ denotes a code fragment of a term of type $\tau$.
An $\alpha$-closed type corresponds to a runnable code fragment.

>>>>

A type is a type variable which is declared in the signature, a dependent function type,
an application of a term to a dependent function type, a code type, or an $\alpha$-closed type.
A function type in ordinary type systems is omitted 
because it is a special case of a dependent type $\Pi x:\tau$, which has no free occurrence of $x$  in $\tau$.
An application of a term to a dependent function type is, for example, $\text{Vector}\ 10$
if type variable $\text{Vector}$ has the kind $\Pi x:\I.*$.
A code type $\TW_\alpha \tau$ denotes a code fragment of a term of type $\tau$.
An $\alpha$-closed type corresponds to a runnable code fragment.
Type constructors tie strongly in the order of 
an application of a term to a dependent function type $\tau\ M$, a dependent function type $\Pi x:\tau.\tau$, 
a code type $\TW_{\alpha} \tau$, an $\alpha$-closed type $\F\alpha.\tau$
Therefore, $\F\alpha.\TW_{\alpha}.\Pi x:\I.\text{Vector}\ 5$ is interpreted as
$\F\alpha.(\TW_{\alpha}.(\Pi x:\I.(\text{Vector}\ 5)))$.
